Supplementary Information

### 2020-08-28 doc/manuscript/MEE_manuscript_SI.Rmd

@@

In either case we need bark thickness--ideally allometries describing the relationship between DBH and bark thickness (Table S4). 
This is especially critical for thick-barked species
When bark thickness data were available, we generated allometries ... 
lognormal model with intercept forced to zero: lm(bark_depth.mm ~ -1 + log(dbh_no_bark.cm+1):bark_species, data = bark)
([issue #8 in ForestGEO_dendro](https://github.com/EcoClimLab/ForestGEO_dendro/issues/8))

@@

@@

Our analysis included two sites where climate change has had pronounced effects on tree growth: Scotty Creek, NW Territories, Canada (SC) and Little Tesuque, New Mexico, USA (LT).
At SC, [temperatures have increased by X $^\circ$ over X years]..., resulting in negative growth trends in basal area index ($BAI$) starting around 1950 and significant growth declines since 1970 in `r round(249/(249+69+127)*100, digits=0)`% of trees [@sniderhan_growth_2016].

@@

>>>>

*This is still rough/ mostly notes.*

@@

In either case we need bark thickness--ideally allometries describing the relationship between DBH and bark thickness (Table S4). 
This is especially critical for thick-barked species.
When bark thickness data were available, we generated allometries ([issue #8 in ForestGEO_dendro](https://github.com/EcoClimLab/ForestGEO_dendro/issues/8))... 
lognormal model with intercept forced to zero: `lm(bark_depth.mm ~ -1 + log(dbh_no_bark.cm+1):bark_species, data = bark)`.
When bark thickness data were not available, we used published bark allometries from other sources (Table S4)

@@

*This is in process. For ~4 selected species (well-studied), we will build chronologies that exactly match the data used in this analysis. We'll then generate a figure like Fig. S1. We expect a pretty good match, as our results are basically consistent with previous studies at all these sites.*

@@

Our analysis included two sites where climate change has had pronounced effects on tree growth: Scotty Creek, NW Territories, Canada (SC) and Little Tesuque, New Mexico, USA (LT).
At SC, [temperatures have increased by X $^\circ$ over X years]..., resulting in negative growth trends in basal area index ($BAI$) starting around 1950 and significant growth declines since 1970 in `r round(249/(249+69+127)*100, digits=0)`% of trees [@sniderhan_growth_2016].
At LT, *(drought has increased dramatically)*, resulting in many missing rings in recent years.

*This is in process. We will try and compare 3 methods: (1) our standard approach, (2) detrending the climate variables (#53), (3) applying the climwin step only for older records--before the most rapid climate change. We will work with SC and LT researchers to determine which makes most sense, and use that as the main approach for these sites.*

@@

This will include:

site | species | n trees (all) | n cores (all) | n trees (DBH) | n cores (DBH) | DBH range: sampled | DBH range: reconstructed | date range | collected by
-- | -- | -- | -- | -- | -- | -- | -- | -- | --
